identifires
===========

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/ropenscilabs/identifires.svg?branch=master)](https://travis-ci.org/ropenscilabs/identifires)
[![codecov.io](https://codecov.io/github/ropenscilabs/identifires/coverage.svg?branch=master)](https://codecov.io/github/ropenscilabs/identifires?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/identifires)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/identifires)](https://cran.r-project.org/package=identifires)

identifiers.org API Client

## identifiers API Docs

See <https://identifiers.org/restws>

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/identifires")
```

```{r}
library("identifires")
```

## Examples

collections

```{r}
idf_collections()
```

resources

```{r eval=FALSE}
idf_resources()
```

validate

```{r eval=FALSE}
idf_validate()
```

metadata

```{r eval=FALSE}
idf_metadata()
```

prefixes

```{r eval=FALSE}
idf_prefixes()
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/identifires/issues).
* License: MIT
* Get citation information for `identifires` in R doing `citation(package = 'identifires')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
